Signal Processing to Demodulate FM Radio

### 2020-12-12 doc/paper/paper.tex
write some stuff

  \subsection{Frequency Modulation (FM)}

@@

  \subsection{Frequency Band}
  %may be used freely, with limited power

  \subsubsection{FM Channel Allocation}

>>>>

  \subsection{Frequency Modulation}
    Frequency modulation (FM) is a modulation method, in which the information content is encoded in the frequency of a signal.
    To be exact, the information is encoded in the frequencies' deviation from the carrier frequency.
    The technology is widely used in FM broadcast radio.
    One of its main advantages over amplitude modulation (AM) is the better signal-to-noise ration (SNR).
    This is achieved, because of the constant amplitude in FM, which makes it less sensitive to additive noise in the transmission channel.
    Additionally, this fact makes it easier for a receiver to synchronize on the received signal.

@@

  \subsection{Frequency Band}
    The frequency band that is used for FM sound broadcasting spans from 87.5 to 108 MHz in Europe. %https://www.itu.int/en/ITU-R/terrestrial/broadcast/Pages/FMTV.aspx
    This range is located within the so-called Very-High-Frequency (VHF) band.
    Anyone may use the specified frequency range freely, with a limited transmission power, as long as neighboring receivers are not disturbed in receiving an existing channel.
    Austria allowed the legal usage in 2006. %CHECK
    As an example, the German Federal Network Agency specifies the power limit as 50 nW, or -43 dBm, of effective radiated power (ERP).
    In a practical usecase, this means that a transmitter needs to select a channel that is not already occupied by an official sender.
    If a free channel is found, the transmitter may start sending a FM signal with the mentioned power limitations.
    %check Wikipedias' sources for my source references/links
    %https://www.conrad.at/de/o/fm-transmitter-1310051.html
    %https://de.wikipedia.org/wiki/FM-Transmitter
    %https://www.ris.bka.gv.at/GeltendeFassung.wxe?Abfrage=Bundesnormen&Gesetzesnummer=20008807
    %https://www.rtr.at/medien/was_wir_tun/frequenzverwaltung/Frequenzen.en.html

  \subsubsection{FM Channel Allocation}
    %each channel:
    % spacing
    % bandwidth
    % specific part of spectrum (see Fig.1)
    % TODO: make Fig1 smaller (cut top/bottom)
    \begin{figure}[!h]
      \centering
        \includegraphics[width=7cm]{img/fm-channel-freqs.png}
      \caption{Block diagram of the entire system.}
      \label{fig_sim}
    \end{figure}
